### 2018-02-28 Sections/cryptowars.tex
restructure

\subsubsection{Digital signatures} \index{Digital signatures}

@@

\subsubsection{Hashing} \index{Hashing}

@@

In the Blockchain protocol, the validity of contracts and transactions is recognised collectively by participants using an encrypted digital ledger. The ledger records the complete history of all Blockchain transactions, which are digitally signed by network participants using elliptic curve public-key cryptography\index{Digital signatures}\index{Elliptic curve cryptography}. A democratic process ensures that, provided a single user doesn't monopolise the network, recorded transactions are legitimate, recognised collectively. This is secured by network participants digitally signing off on transactions as they take place.

>>>>

\subsubsection{Digital signatures} \label{sec:dig_sig} \index{Digital signatures}

@@

\subsubsection{Hashing} \label{sec:hashing} \index{Hashing}

@@

In the Blockchain protocol, the validity of contracts and transactions is recognised collectively by participants using an encrypted digital ledger. The ledger records the complete history of all Blockchain transactions, which are digitally signed (Sec.~\ref{sec:hashing}) by network participants using elliptic curve public-key cryptography\index{Digital signatures}\index{Elliptic curve cryptography}. A democratic process ensures that, provided a single user doesn't monopolise the network, recorded transactions are legitimate, recognised collectively. This is secured by network participants digitally signing off on transactions as they take place.
